Paper_stuff

### 2024-02-19 Paper_stuff.Rmd
Anxiety & Depression seperate LASSO

Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
head(df)
```

@@

@@

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  scale_fill_discrete(name = "Education") +
  coord_polar("y",start=0)+
  theme_void()
```

>>>>

Read in the dataset. 
```{r}
Mothership1 <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
head(df)
mode(Mothership1$Relationship_1)
```

@@

relationship
```{r}
ggplot(data = subset(Mothership_post, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Gender") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Gender")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  coord_flip()+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

Mothership_post$Relationship_1

ggplot(data = subset(Mothership_post, !is.na(Relationship_1)),mapping = aes(x = Relationship_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Relationship") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("relationshipr")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  coord_flip()+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

summary(Mothership_post$Relationship_1)

@@

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  scale_fill_discrete(name = "Education") +
  coord_polar("y",start=0)+
  theme_void()

Mothership_post
```
